Rotations and Insecticide Resistance the story

### 2019-03-12 inst/documents/rotations_notes.Rmd
notes

@@

~ change origin of git repo in RStudio, probably need to do from git

>>>>

12/03/19
~ change origin of git repo in RStudio, probably need to do from git
remote: This repository moved. Please use the new location:        
remote:   git@github.com:AndySouth/rotations.git    
from the commandline :
git remote rm origin
git remote add origin git@github.com:AndySouth/rotations.git

@@
